On exponential sums arising from the classical doubling method

### 2025-03-14 paper.tex
Trying to prove that the function after intertwining operator vanishes outside of the parabolic

% Matrices macros
\newcommand{\transpose}[1]{\, {}^{t}#1}
\newcommand{\inverseTranspose}[1]{#1^{\iota}}
\newcommand{\involution}[1]{#1^{c}}
\newcommand{\minusInvolution}[1]{#1^{-c}}
\newcommand{\involutionPlusOne}[1]{#1^{1+c}}
\newcommand{\IdentityMatrix}[1]{I_{#1}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\antidiag}{\operatorname{\mathrm{antidiag}}}
\newcommand{\trace}{\operatorname{tr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\SO}{\mathrm{SO}}
\newcommand{\GSO}{\mathrm{GSO}}
\newcommand{\Sp}{\mathrm{Sp}}
\newcommand{\GSp}{\mathrm{GSp}}
\newcommand{\UnitaryGroup}{\mathrm{U}}
\newcommand{\UnipotentSubgroup}{U}
\newcommand{\UnipotentRadical}{N}
\newcommand{\ParabolicSubgroup}{P}
\newcommand{\GroupExtension}[1]{\widetilde{#1}}

@@

Let $\xIsotropic$ and $\yIsotropic$ be isotropic spaces of $\hermitianSpace$ of dimension $k$, such that $\xIsotropic$ and $\yIsotropic$ are in duality with respect to form $\innerproduct{\cdot}{\cdot}$. Let us write $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
where $\hermitianSpace' \subset \hermitianSpace$ is a non-degenerate subspace, orthogonal to $\xIsotropic$ and $\yIsotropic$. Let $P$ be the parabolic subgroup of $H$, consisting of all elements stabilizing the flag $$0 \subset \xIsotropic \subset \xIsotropic \oplus \hermitianSpace' \subset \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic = \hermitianSpace.$$
Let $G' = \IsometryGroup\left(\hermitianSpace'\right)$. Write $P = L \ltimes N$, where $L$ is the Levi part of $P$ and $N$ is the unipotent radical of $P$. Then $L$ is isomorphic to $H' \times \GL_k\left(\quadraticExtension\right)$, where $H' \in \left\{G',\GroupExtension{G'}\right\}$ is of the same type as $H$.

@@

	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
	which can be rewritten as
	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
	As before, we may write
	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic \left(-h\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h\right)\right)\right).$$
	Hence, \begin{align*}
		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \\
		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Assume that $\chi \ne 1$. By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$. Let us replace $h$ with $A^{-1} h$. We get the sum
	\begin{align*}
		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A x l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
	The inner sum over $N$ will vanish unless $Ax \in P$. Thus we have
	\begin{align*}
		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p - x^{-1} \in P$, which implies that $x \in P \cap G$.

	Hence, we have that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. We move to compute $\left(\dblJacobiSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
				\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} - p\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
	\end{equation}
	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(\idmap_{\hermitianSpace} - p\right) = \left(-1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(\IdentityMatrix{k} - a\right) \det\left(\involution{\left(\IdentityMatrix{k} - a\right)}\right) \detQuadratic\left(\idmap_{\hermitianSpace'} - g'\right),$$
	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
	\begin{equation}
		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \Phi_{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
	\end{equation}
	which in turn is
	\begin{align*}
		&\chi\left(-1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
		=& \chi\left(-1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
	\end{align*}
	The result now follows.
\end{proof}

@@

\appendix
\section{Evaluation of norm one exponential sums}

>>>>

% Matrices macros
\newcommand{\transpose}[1]{\, {}^{t}#1}
\newcommand{\inverseTranspose}[1]{#1^{\iota}}
\newcommand{\involution}[1]{#1^{c}}
\newcommand{\minusInvolution}[1]{#1^{-c}}
\newcommand{\involutionPlusOne}[1]{#1^{1+c}}
\newcommand{\IdentityMatrix}[1]{I_{#1}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\antidiag}{\operatorname{\mathrm{antidiag}}}
\newcommand{\trace}{\operatorname{tr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\SO}{\mathrm{SO}}
\newcommand{\GSO}{\mathrm{GSO}}
\newcommand{\Sp}{\mathrm{Sp}}
\newcommand{\GSp}{\mathrm{GSp}}
\newcommand{\UnitaryGroup}{\mathrm{U}}
\newcommand{\UnipotentSubgroup}{U}
\newcommand{\UnipotentRadical}{N}
\newcommand{\ParabolicSubgroup}{P}
\newcommand{\GroupExtension}[1]{\widetilde{#1}}
\newcommand{\Center}{\mathrm{Z}}

@@

Let $\xIsotropic$ and $\yIsotropic$ be isotropic spaces of $\hermitianSpace$ of dimension $k$, such that $\xIsotropic$ and $\yIsotropic$ are in duality with respect to form $\innerproduct{\cdot}{\cdot}$. Let us write $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
where $\hermitianSpace' \subset \hermitianSpace$ is a non-degenerate subspace, orthogonal to $\xIsotropic$ and $\yIsotropic$. Let $P = P_{H}\left(\mathcal{F}\right)$ be the parabolic subgroup of $H$, consisting of all elements stabilizing the flag \begin{equation}\label{eq:definition-of-flag-for-parabolic-subgroup}
	\mathcal{F} \colon 0 \subset \xIsotropic \subset \xIsotropic \oplus \hermitianSpace' \subset \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic = \hermitianSpace.
\end{equation}
Let $G' = \IsometryGroup\left(\hermitianSpace'\right)$. Write $P = L \ltimes N$, where $L$ is the Levi part of $P$ and $N$ is the unipotent radical of $P$. Then $L$ is isomorphic to $H' \times \GL_k\left(\quadraticExtension\right)$, where $H' \in \left\{G',\GroupExtension{G'}\right\}$ is of the same type as $H$.

@@

	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
	which can be rewritten as
	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
	As before, we may write
	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic \left(-h\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h\right)\right)\right).$$
	Hence, \begin{equation}
		\begin{split}\label{eq:gamma-factor-multiplicativity-support-expression}
			& \chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) \\
			= & \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(x^{-1}p - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
		\end{split}
	\end{equation}
	Assume that $\chi \ne 1$. By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$. Let us replace $h$ with $A^{-1} h$. We get the sum
	\begin{align*}
		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(x^{-1} p - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Replace the sum over $p \in P$ by a sum over $l \in L$ and $u \in N$ where $p = lu$ and change variables $u \mapsto u^{-1}$ and $A \mapsto A u$. We arrive at the sum
	\begin{align*}
		\sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{l \in L} \sum_{u \in U} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(x^{-1} l - u\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).
	\end{align*}
	Using the appendix, we arrive at the sum
	\eqref{eq:gamma-factor-multiplicativity-support-expression} is given by
	\begin{align*}
		& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
		& \times \sum_{A \in P_{\GL_{\quadraticExtension}\left(\mathcal{F}\right)}} \sum_{p \in P} \chi^{-1}\left(\detQuadratic A\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(x^{-1} p - \idmap_{\hermitianSpace} \right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right),
	\end{align*}
	Where $P_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)$ is the parabolic subgroup of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$ stabilizing the flag $\mathcal{F}$ from \eqref{eq:definition-of-flag-for-parabolic-subgroup}. By decomposing the sum over $A$ into a sum over its Levi part and its unipotent radical, we see that the inner sum over the unipotent radical will vanish unless $x^{-1} p - \idmap_{\hermitianSpace}$ is an upper triangular matrix, which implies that $x \in P \cap G$.

	Hence, we have that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. We move to compute $\left(\dblJacobiSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
				\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} - p\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
	\end{equation}
	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(\idmap_{\hermitianSpace} - p\right) = \left(-1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(\IdentityMatrix{k} - a\right) \det\left(\involution{\left(\IdentityMatrix{k} - a\right)}\right) \detQuadratic\left(\idmap_{\hermitianSpace'} - g'\right),$$
	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
	\begin{equation}
		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \Phi_{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
	\end{equation}
	which in turn is
	\begin{align*}
		&\chi\left(-1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
		=& \chi\left(-1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
	\end{align*}
	The result now follows.
\end{proof}
\begin{remark}
	A proof similar to the second part of our proof is given in \cite{Chang1997}. However, the proof in \cite{Chang1997} only works if the parabolically induced representation is irreducible.
\end{remark}

@@

\appendix
\section{Unipotent averaging}

Choose bases $e_1,\dots,e_k$ for $\xIsotropic$ and $f_1,\dots,f_k$ for $\yIsotropic$ that are dual, i.e., $\innerproduct{e_i}{f_j} = \delta_{ij}$, where $\delta_{ij}$ is Kronecker's delta function, and choose a basis $v'_1, \dots, v'_{r}$ for $\hermitianSpace'$. Then with respect to the basis $e_1,\dots,e_k,v_1',\dots,v_r',f_k,f_{k-1},\dots,f_1$, elements in $N$ can be represented in matrix form $$\begin{pmatrix}
	\IdentityMatrix{k} & X & Z\\
	& \IdentityMatrix{r} & Y\\
	& & \IdentityMatrix{k}
\end{pmatrix},$$
where $X,Y$ and $Z$ are matrices satisfying certain relations. Under this realization, the center $\Center\left(N\right)$ of $N$ corresponds to matrices of the form \begin{equation}\label{eq:center-matrix-representation}
	\begin{pmatrix}
		\IdentityMatrix{k} & 0 & Z\\
		& \IdentityMatrix{r} & 0\\
		& & \IdentityMatrix{k}
	\end{pmatrix},
\end{equation}
where $Z$ is a certain type of matrix: it is ``-$\epsilon$ symmetric'', that is, it satisfies $$Z = -\epsilon w_k \involution{\left(\transpose{Z}\right)} w_k,$$
where $$w_k = \begin{pmatrix}
	& & & 1\\
	& & 1\\
	& \iddots\\
	1
\end{pmatrix} \in \GL_k\left(\finiteField\right)$$ is the long Weyl element.

The following sum appears as an inner sum in \eqref{TODO}:
\begin{equation}\label{eq:sum-that-vanishes-unless-A-is-upper-triangular}
	\sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(-Au\right)\right) = \sum_{u \in N \slash \Center\left(N\right)} \fieldCharacter_{\quadraticExtension}\left(\trace\left(-Au\right)\right) \sum_{z \in \Center\left(N\right)} \fieldCharacter_{\quadraticExtension}\left(\trace\left(-Az\right)\right).
\end{equation}
Consider the inner sum 
\begin{equation*}
	\sum_{u \in Z\left(N\right)} \fieldCharacter_{\quadraticExtension}\left(\trace\left(-Az\right)\right).
\end{equation*}
This sum vanishes unless the matrix representation of $A$ is of the form $$\begin{pmatrix}
	a_{k \times k} & a'_{k \times r} & a''_{k \times k} \\
	b_{r \times k} & b'_{r \times r} & b''_{r \times k}\\
	c_{k \times k} & c'_{k \times r} & c''_{k \times k}
\end{pmatrix},$$
where $c_{k \times k}$ is ``$\epsilon$-symmetric'', that is, it satisfies \begin{equation}\label{eq:epsilon-symmetric-relation}
	c_{k \times k} = \epsilon w_k \involution{\left(\transpose{c_{k \times k}}\right)} w_k.
\end{equation}
Let us denote by $R$ the subset of $\EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)$ consisting of elements such that their matrix representation satisfies the relation \eqref{eq:epsilon-symmetric-relation}.
Then we may replace the sum
$$\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(x^{-1} l - u\right)\right)\right)$$ with 
$$\sizeof{\Center\left(N\right)} \sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right) \cap R} \chi^{-1}\left(\detQuadratic A\right) \sum_{u \in N \slash \Center\left(N\right)} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(x^{-1} l - u\right)\right)\right).$$
Let $N_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)$ be the unipotent radical of the parabolic subgroup $P_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)$ of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$ stabilizing the flag $\mathcal{F}$. Its center $\Center\left(N_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)\right)$ consists of linear maps whose matrix representation is of the form \eqref{eq:center-matrix-representation}, where $Z$ is an arbitrary matrix.

We notice the following observation: if $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right) \cap R$, then for any $z \in \Center\left(N_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)\right)$, we have $zA \in \GL_{\quadraticExtension}\left(\hermitianSpace\right) \cap R$. This is because the left action of $\Center\left(N_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)\right)$ does not change the last $k$ rows of $A$. It follows that $\GL_{\quadraticExtension}\left(\hermitianSpace\right) \cap R$ is a union of left (or right) cosets of $\Center\left(N_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)\right)$.

$P_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)$ is the parabolic subgroup of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$ that stabilizes the flag $\mathcal{F}$ from \eqref{eq:definition-of-flag-for-parabolic-subgroup}.

\section{Evaluation of norm one exponential sums}
